\section{Homomorphic encryption}

Goal: Compute on encrypted data with no interaction between user and cloud.

\subsection{Single homomorphic encryption}

Encryption scheme supporting operation $\oplus$ such that $Enc(x) \oplus Enc(y)
= Enc(x + y)$, or operation $\otimes$ such that $Enc(x) \otimes Enc(y) = Enc(x
\cdot y)$, where $x, y$ from some finite field of prime order.

Examples: Additively homomorphic ElGamal.

\subsection{Multiplicatively homomorphic ElGamal}

Textbook ElGamal is already multiplicatively homomorphic. Let $(R, C) = (g^r, m
\cdot y^r), (R', C') = (g^{r'}, m \cdot y^{r'})$ be two ciphertexts. Then the
component-wise multiplication $(\hat{R}, \hat{C}) = (g^{r + r'}, m \cdot m'
\cdot y^{r + r'})$ is a valid encryption of $m \cdot m'$.

\subsubsection{Additively homomorphic ElGamal}

Using $Enc$ and $Dec$ of textbook ElGamal, let:

\begin{algorithm}
		\caption{AM-ElGamal}
		\begin{algorithmic}[0]
				\Procedure{AM-Enc}{$y, m$}
						\State \textbf{Return} $\operatorname{Enc}(y, g^m)$
				\EndProcedure

				\Procedure{AM-Dec}{$x, (R, C)$}
						\State $h \coloneqq \operatorname{Dec}(x, (R, C))$
						\For{$i \gets 0, max$}
								\If{$g^i = h$}
										\State \textbf{Return} $i$
								\EndIf
						\EndFor
						\State \textbf{Return} error
				\EndProcedure
		\end{algorithmic}
\end{algorithm}

\subsection{Voting protocol using AM ElGamal}

\begin{itemize}
		\item Parties $P_i$ with votes $v_i$, authority $A$
		\item $A$ generates keypair, distributes public key
		\item $A$ computes $c_0 = \operatorname{Enc}(pk, 0)$ and sends to $P_1$
		\item $P_i$ computes $c_i = c_{i-1} \oplus Enc(y, v_i)$ and sends to
				$P_{i+1}$ ($P_n$ sends to $A$)
		\item $A$ decrypts $z = \operatorname{Dec}(x, c_n)$
		\item $A$ publishes $z = \sum_{i = 1}^n v_i$
\end{itemize}

Note:
\begin{itemize}
		\item Not robust against malicious parties. They can encrypt values
				other than $0, 1$, refuse to send the ciphertext on (or send
				malicious values), or $A$ can refuse to decrypt.
		\item Defenses: ZKP to prove valid vote, public bulletin board for
				communciation, distributed implementation of $A$ using secret
				sharing.
\end{itemize}

\section{Zero-knowledge proofs}

Prove statement is true, or knowledge of information, without giving away any
more information. Two kinds:

\begin{description}
		\item[Proof for statement] E.g. given boolean formula, there exists a
				set of variables such that it evaluates to true. Given two
				graphs, they are isomorph. Given a graph, there exists a
				hamiltonian circuit.
		\item[Proof of knowledge] Given $y$, I know $x$ such that $y = g^x$.
				Given a binary string $h$, I know $x$ such that $H(x) = h$.
				Given $n$ I know $p, q$ such that $n = pq$.
\end{description}

Requirements:
\begin{description}
		\item[Completness] If $S$ holds, prover $P$ correct, verifier $V$
				correct, then $V$ accepts.
		\item[Soundness] If $S$ false, then honest verifier $V$ will reject
				with at least a constant non-zero probability.
		\item[Zero-knowledge] $V$ learns only that $S$ holds, and not more.
\end{description}

For proof, show that:
\begin{description}
		\item[Completness] It holds with $P, V$ honest
		\item[Soundness] Given $P$ malicious, $V$ will reject with at least
				constant non-zero probability.
		\item[Zero knowledge] $V$ can also generate output with same
				distribution as protocol on its own (if in different order).
\end{description}

\subsection{Graph isomorphism}

$P$, $V$ given two graphs $G_0 = (V, E_0), G_1 = (V, E_1)$. $P$ knows an
isomorphism $f$ between the two, i.e. a bijective $f: V \rightarrow V$ such that
$\forall v, w \in V: (v, w) \in E_0 \Leftrightarrow (f(v), f(w)) \in E_1$.

\subsubsection{Protocol}

\begin{enumerate}
		\item $P$ chooses random permutation $\Pi$ on $V$, computes $H = (V,
				F)$ such that $H$ is isomorphic to $G_0$. Sends $H$ to $V$.
		\item $V$ sends random bit $b$
		\item $P$ shows isomorphism $\rho = \Pi$ for $b = 0$, $\rho = \pi \circ
				f^{-1}$ for $b = 1$.
		\item $V$ checks if $G_b$ is isomorphic to $H$.
\end{enumerate}
