\subsection{Threshold ElGamal}

Idea: Encrypt such that any $f+1$ clients together can decrypt the ciphertext.
For key generation, have trusted party distribute shares of private key $x
\leftrightarrow (x_1, \ldots, x_n$) using $f+1$-out-of-$n$ secret sharing.

For encryption, regular hashed ElGamal, $R \coloneqq g^r, C \coloneqq H(y^r)
\oplus m$.

For decryption:
\begin{itemize}
		\item Client sends $(R, C)$ to all parties $P_1, \ldots, P_n$
		\item Party $P_i$ computes $d_i \coloneqq R^{x_i}$ and sends to client
		\item Having received $f+1$ decryption shares, the client computes $z
				\coloneqq \prod d_i^{\lambda^s_{0,i}}$. Now $z = y^r$, so it
				computes $\hat{m} \coloneqq H(z) \oplus C$ and $\hat{m} = m$
\end{itemize}

Secure against passive attacks due to properties of secret sharing scheme. Not
robust against malicious parties, as they can release incorrect decryption
shares.

\subsubsection{Robustness against malicious parties}

Dealer generates $y = g^x$ and $y_i = g^{x_i}$ for every party $P_i$. $y_i$ is
publicly released. Then, every party $P_i$ has to additionally prove --- using
a ZKPK --- that it knows the $x_i$ such that $y_i = g^{x_i} \land d_i =
R^{x_i}$.

\subsection{RSA threshold signatures}

Recall: RSA does have a group homomorphism, but we cannot use it as $\varphi(N)$
must not be public. Instead, use $n$-of-$n$ secret sharing over the integers.

\subsubsection{Key generation}

To share secret key $d$, choose random $d_i \rgets [0, N \cdot 2^\lambda]$ such
that $\sum d_i \equiv d \pmod{\varphi(N)}$, with $\lambda = 128$.


\subsubsection{Distributed signature generation}

\begin{itemize}
		\item Every party computes and sends a signature share $\sigma_i
				\coloneqq H(m)^{d_i} \mod N$ to client.
		\item Upon having received $n$ shares, client computes $\sigma
				\coloneqq \prod \sigma_i \mod N$
\end{itemize}


\subsubsection{Impracticality}

Issues:
\begin{itemize}
		\item Only supports $n$-out-of-$n$ secret sharing
		\item Other schemes exist for $f+1$-out-of-$n$ RSA signatures
\end{itemize}

\subsection{Proactive security}

Issue: Over long time, shares are bound to be compromised. Once more than $f$
shares exposed, security is lost.

Idea: Work in epoch. Once per epoch, reshare the secret. Then, as long as fewer
than $f$ shares are lost per epoch, security holds.

\begin{itemize}
		\item Let $x$ be secret, $a(x) = (x_1, \ldots x_n)$ the current shraing
		\item Let $a'(x) = (x'_1, \ldots, x'_n)$ be a new sharing, that is
				$a(0) = a'(0)$. How to generate $a'$ in distributed way?

		\item Each $P_i$ generates a random sharing $b_i(x)$ of $0$, and sends
				the share $b_i(j)$ to every party $P_j$
		\item Then each $P_i$ calculates $x'_i \coloneqq \sum b_j(i) + x_i$
		\item Now, $x'_i$ will be a share for $a'(x)$.
\end{itemize}
